---
title: "ApplianceSalePred"
author: "BalajiK"
date: "June 1, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data extraction

### Data Source
Source:
Dr Daqing Chen, Director: Public Analytics group. chend '@' lsbu.ac.uk, School of Engineering, London South Bank University, London SE1 0AA, UK

Courtesy:
Daqing Chen, Sai Liang Sain, and Kun Guo, Data mining for the online retail industry: A case study of RFM model-based customer segmentation using data mining, Journal of Database Marketing and Customer Strategy Management, Vol. 19, No. 3, pp. 197–208, 2012 (Published online before print: 27 August 2012. doi: 10.1057/dbm.2012.17).
###

```{r}
setwd("~/R/xpo_h3")
raw1 <- read.csv("Online Retail.csv", header = TRUE)
read.csv()
summary(raw1)
library(dplyr)
raw2 <- select(.data = raw1,c(2,4,5,8))
names(raw2)
```

## Data partitioning 

```{R}
library(caret)
intrain <- createDataPartition(y = raw2,p = 0.7,list = FALSE)
```

## Defining model to predict Sales for appliance types for entered zip code.

```{r Statistical_modelling, echo=FALSE}
modelname <- lm(sales, factor(appliance) * month, data=raw1)
```

